### 2020-04-02 draft.tex
definition of arrow (for things to come)

@@

>>>>

\begin{defn}
  We let $\downarrow$ be the walking arrow --- the category $\term{dom} \to
  \term{cod}$ consisting of a single morphism. We denote by $\sigma : \downarrow
  \to \downarrow\op$ the self-dualizing isomorphism of $\downarrow$, and note
  that $\sigma\inv = \sigma\op$.
\end{defn}

@@

In this section, we will categorify Dirichlet series
$$\sum_{n \in \Nb} a_n n^{-s}.$$

First, we review the notion of \emph{homotopy cardinality}.

\begin{defn}
Let $B$ be a homotopy type. We define the \emph{homotopy cardinality} $#B$ to be
the following sum:
$$#B := \sum_{[b] \in \pi_0(B)} \prod_{n = 1}^{\infty} |\pi_n(B, b)|^{(-1)^n}$$

We note that
$$#B = \sum_{[b] \in \pi_0(B)} \frac{1}{#\Omega(B, b)}$$
\end{defn}

We will leave questions concerning the convergence and well-definedness of the
homotopy cardinality of a type, noting only that if a type $B$ is totally finite in
that it has finitely many connected components, its homotopy groups are finite,
and they eventually vanish, then $#B$ is a finite sum of a finite product and so
is well defined.

The main lemma concerning homotopy cardinality is its behavior with respect to
fibrations.
\begin{lem}
Let $\pi : E \to B$ be a map of homotopy types, and let $E_b$ denote the fiber
over $b : B$. Then
$$#E = \sum_{[b] \in \pi_0(B)}\frac{#E_b}{#\Omega(B, b)}.$$
As a corollary:
\begin{enumerate}
\item $#(A \times B) = #A \cdot #B$ and so $#(B^n) = (#B)^n$.
\item If $B$ is pointed and connected and $F$ is the fiber of $\pi$ over the
  basepoint, then $#E = #F \cdot #B$.
\item If $A_n$ is a family of types for $n : \Nb$, then $#(\sum_n A_n) = \sum_n #A_n$.
\end{enumerate}
\end{lem}
\begin{proof}
  We note that by the long exact sequence of homotopy groups, we have that
  $$|\pi_n(E, e)| = |\pi_n(E_{\pi e}, e)|\cdot |\pi_n(B, \pi e)|$$
  Therefore, we may calculate
  \begin{align*}
    #E &= \sum_{[e] \in \pi_0(E)}\prod_{n=1}^{\infty} |\pi_n(E, e)|^{(-1)^n}\\
    &= \sum_{[b] \in \pi_0(B)} \sum_{[e] \in \pi_0(E_b)} \prod_{n=1}^{\infty} (|\pi_n(E_{b}, e)|\cdot |\pi_n(B, b)|)^{(-1)^n}\\
    &= \sum_{[b] \in \pi_0(B)}\prod_{n=1}^{\infty} |\pi_n(B, b)|^{(-1)^n} \sum_{[e] \in \pi_0(E_b)} \prod_{n=1}^{\infty} |\pi_n(E_{b}, e)|^{(-1)^n}\\
    &= \sum_{[b] \in \pi_0(B)}\frac{#E_b}{\frac{#\Omega(B, b)}}.
  \end{align*}

  We may then take various maps $\pi : E \to B$ to recover the corollaries:
  \begin{enumerate}
  \item Take the projection $A \times B \to B$.
  \item Take the map $\pi : E \to B$, noting that if $B$ is pointed connected then $#B =
    \frac{1}{\Omega B}$.
  \item Take the projection $\sum_n A_n \to \Nb$.
  \end{enumerate}
\end{proof}

Now, we note that if $B$ is connected, then $#B = \frac{1}{#\Omega(B, b)}$ for
any point $b : B$. Therefore, if $B$ is connected with finite homs of
cardinality $n$, then $#B = \frac{1}{n}$ and so $#(B^s) = n^{-s}$. This is the
observation --- originally due to Baez and Dolan in \emph{This Weeks Finds}
(cite) --- that we will use to categorify Dirichlet series.

\begin{defn}
A homotopy type $B$ is \emph{locally finite and connected}, or \emph{lfc}, if it
is $0$-connected and its homs are finite.

We denote by $\type{lfc}$ the homotopy type of lfc types, and note that the
bundle $\fst : \type{lfc}_{\ast} \to \type{lfc}$ forgetting the point of a
pointed lfc type classifies maps with lfc fibers.
\end{defn}
